The ChEMBL database as Linked Open Data

### 2012-03-07 article.tex
Added the main ChEMBL paper

ChEMBL contains biological activities for over a million chemical entities, extracted from
literature, providing a unique resource for drug discovers~\cite{Warr2010}. Originally, this
data was available for download and via a web interface. The former requires setting up
the data in a relational database, while the latter limits the machine access to the data.
Two independent teams created RDF triples for the ChEMBL data, resulting in exposure
via Chem2Bio2RDF~\cite{} and ChEMBL-RDF~\cite{Willighagen2011}.

>>>>

ChEMBL contains biological activities for over a million chemical entities, extracted from
literature, providing a unique resource for drug discovers~\cite{Gaulton2012,Warr2010}. Originally, this
data was available for download and via a web interface. The former requires setting up
the data in a relational database, while the latter limits the machine access to the data.
Two independent teams created RDF triples for the ChEMBL data, resulting in exposure
via Chem2Bio2RDF~\cite{} and ChEMBL-RDF~\cite{Willighagen2011}.
